Early Warning Signals and the Prosecutor's Fallacy

### 2012-08-30 prosecutor/fallacy.tex
fixed equation formating

\section{Methods and Results}
To investigate if early warning signals are vulnerable to this fallacy,
we simulate a system that is not driven towards a bifurcation such as
in Fig~\ref{fig:fallacy}.  This simulation approach allows us to determine whether
examining historical events is a valid way to test the utility of these
indicators.  We simulated 20,000 replicates of a stochastic individual-based
birth-death process with an Allee threshold~\citep{Courchamp2008}, which
arises from positive fitness effects at low densities.  Above the Allee
threshold the population returns to a positive equilibrium size, whereas
below the threshold the population decreases to zero. The model can be represented as a continuous time birth-death process where births and deaths are Poisson events whcih depend on the current density,

\begin{align}
    b(X) &= \frac{e K n^2}{n^2 + h^2}, \\
    d(X) &= e n + a,

\end{align}

>>>>

\section{Methods and Results}
To investigate if early warning signals are vulnerable to this fallacy,
we simulate a system that is not driven towards a bifurcation such as
in Fig~\ref{fig:fallacy}.  This simulation approach allows us to determine whether
examining historical events is a valid way to test the utility of these
indicators.  We simulated 20,000 replicates of a stochastic individual-based
birth-death process with an Allee threshold~\citep{Courchamp2008}, which
arises from positive fitness effects at low densities.  Above the Allee
threshold the population returns to a positive equilibrium size, whereas
below the threshold the population decreases to zero. The model can be represented as a continuous time birth-death process where births and deaths are Poisson events which depend on the current density with rates given by

\begin{align}
    b(n) &= \frac{e K n^2}{n^2 + h^2}, \label{master} \\
    d(n) &= e n + a, 
\end{align}
